Reproducible Research: Peer Assignment 1
========================================================
## Loading and preprocessing the data
```{r echo=TRUE}
actdata<-read.csv("./data/activity.csv")


```

## What is mean total number of steps taken per day?
1.Make a histogram of the total number of steps taken each day
```{r echo=TRUE}
library(plyr)
sumsteps<-ddply(actdata, ~date, summarize, total=sum(steps, na.rm=TRUE))
timeconvert<-strptime(sumsteps$date, format="%Y-%m-%d")
plot(x<-timeconvert, y<-sumsteps$total, type = "h", lwd=3, col="green", main = "Histogram of the total number of steps taken each day", xlab="Date", ylab="Total number of steps")
```
2.Calculate and report the mean and median total number of steps taken per day

```{r echo=TRUE}
mean(sumsteps$total)
median(sumsteps$total)

```

## What is the average daily activity pattern?

1.Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r echo=TRUE}
avgsteps<-ddply(actdata, ~interval, summarize, avg=mean(steps, na.rm=TRUE))
plot(x<-avgsteps$interval, y<-avgsteps$avg, type = "l", lwd=3, col="red", main="Average daily activity pattern", xlab="Interval", ylab="Average number of steps")
```
2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r echo=TRUE}
avgsteps$interval[which.max(avgsteps$avg)]
```

## Imputing missing values

1.Total number of missing values in the dataset 
```{r echo=TRUE}
sum(is.na(actdata))

```

2.Filling in all of the missing values in the dataset by using the mean for that day.
3.Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r echo=TRUE}
daymean <- ddply(actdata, ~interval, summarize, med = median(steps, na.rm=TRUE))

data2<-actdata

for (i in 1:nrow(data2)) {
  
  if (is.na(data2$steps[i])) {
  
asd<-daymean$interval==data2$interval[i];

data2$steps[i]<-daymean$med[asd]
      }
}

```
4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
```{r echo=TRUE}

sumsteps2 <- ddply(data2,~date,summarize,total=sum(steps,na.rm=TRUE))

 timeconvert2<-strptime(sumsteps2$date, format="%Y-%m-%d")

plot(x<-timeconvert2, y<-sumsteps2$total, type = "h", lwd=3, col="blue",main="Histogram
of the total number of steps taken each day",xlab="Date", ylab="Total number of steps")
```

```{r}
mean(sumsteps2$total)
median(sumsteps2$total)

```

```
Do these values differ from the estimates from the first part of the assignment?
Yes
What is the impact of imputing missing data on the estimates of the total daily number of steps?
mean and is different, and meadian the same


## Are there differences in activity patterns between weekdays and weekends?

```{r}
arg1<- strptime(sumsteps2$date, format="%Y-%m-%d")
data2$isWeekDay <- "weekday"
 Wknd <- weekdays(arg1) == "Saturday" | weekdays(arg1) == "Sunday"
data2$isWeekDay[Wknd] = "weekend"

dWeekend <- ddply(data2[data2$isWeekDay=="weekend",],~date,summarize,avg=mean(steps,na.rm=TRUE))
tst <- ddply(data2,.(isWeekDay, interval),summarize,avg=mean(steps,na.rm=TRUE))


par( mfrow = c( 2, 1 ) )
plot(x<-tst[tst$isWeekDay=="weekday",]$interval, y<-tst[tst$isWeekDay=="weekday",]$avg, type = "l",xlab="interval",ylab="avg number of steps",main="Weekday")
plot(x<-tst[tst$isWeekDay=="weekend",]$interval, y<-tst[tst$isWeekDay=="weekend",]$avg, type = "l",xlab="interval",ylab="avg number of steps",main="Weekend")

```

